Measuring Directionality in Double Beta Decay and Neutrino Interactions with Kiloton-Scale Scintillation Detectors

### 2013-07-22 Direction_v6.tex
Version 6 of draft. Changed event to hit in two sentences. --Christoph

The timing studies show that in the early time window, $t\leq$
34.0~ns, the ratio $R_{C/S}$ is high, improving the event selection. In this section, we apply
reconstruction tools for a water Cherenkov detector, WCSimAnalysis,
to the problem of reconstructing the position and direction of 5~MeV
electrons from this early light.  WCSimAnalysis is a water Cherenkov
reconstruction package developed for the Long Baseline Neutrino
Experiment (LBNE collaboration)\cite{Blake}. It provides a framework
for generic event cleaning, track reconstruction, and particle
identification, and comes equipped with variety of pre-built
algorithms. It is continuing to be expanded using new track-fitting
techniques for water Cherenkov detectors\cite{Sanchez2012525} based on
advanced photosensors with sub-cm imaging capabilities and timing
resolutions below 100 picoseconds\cite{LAPPDSum,LAPPDTDR}.

@@

For the purpose of testing the reconstruction algorithm we use 1000
simulated electrons with an energy of 5~MeV. The electrons are
simulated at the center of the detector, $\vec{r}$ = (0,0,0), along
the x-axis, $\frac{\vec{p}}{|\vec{p}|}$ = (1,0,0). Figure~\ref{fig:reco}
shows the vertex reconstruction. The vertex is reasonably well
reconstructed around the center of the detector, $\vec{r}$ = (0,0,0),
except along the x-axis. The RMS values of the distributions for all three
reconstructed coordinates are smaller than 3.5~cm. The shift along
the x-axis is due to two effects for which the reconstruction has to
use average values rather than the unknown true value for each
event: the wavelength and hence the speed of the light in the medium,
and the point of emission for each of the photons, reconstructed
as coming from a common point. The reconstruction of the direction
also is shown in Fig.~\ref{fig:reco}. It shows that for the majority
of the events the initial electron direction is reconstructed well.
This is a promising result given the simplicity of the algorithms
used.

>>>>

The timing studies show that in the early time window, $t\leq$
34.0~ns, the ratio $R_{C/S}$ is high, improving the photoelectron hit selection. In this section, we apply
reconstruction tools for a water Cherenkov detector, WCSimAnalysis,
to the problem of reconstructing the position and direction of 5~MeV
electrons from this early light.  WCSimAnalysis is a water Cherenkov
reconstruction package developed for the Long Baseline Neutrino
Experiment (LBNE collaboration)\cite{Blake}. It provides a framework
for generic event cleaning, track reconstruction, and particle
identification, and comes equipped with variety of pre-built
algorithms. It is continuing to be expanded using new track-fitting
techniques for water Cherenkov detectors\cite{Sanchez2012525} based on
advanced photosensors with sub-cm imaging capabilities and timing
resolutions below 100 picoseconds\cite{LAPPDSum,LAPPDTDR}.

@@

For the purpose of testing the reconstruction algorithm we use 1000
simulated electrons with an energy of 5~MeV. The electrons are
simulated at the center of the detector, $\vec{r}$ = (0,0,0), along
the x-axis, $\frac{\vec{p}}{|\vec{p}|}$ = (1,0,0). Figure~\ref{fig:reco}
shows the vertex reconstruction. The vertex is reasonably well
reconstructed around the center of the detector, $\vec{r}$ = (0,0,0),
except along the x-axis. The RMS values of the distributions for all three
reconstructed coordinates are smaller than 3.5~cm. The shift along
the x-axis is due to two effects for which the reconstruction has to
use average values rather than the unknown true value for each
hit: the wavelength and hence the speed of the light in the medium,
and the point of emission for each of the photons, reconstructed
as coming from a common point. The reconstruction of the direction
also is shown in Fig.~\ref{fig:reco}. It shows that for the majority
of the events the initial electron direction is reconstructed well.
This is a promising result given the simplicity of the algorithms
used.
